\section{\textsf{Optimization}}
    In this modeling of the absorber the optimization is already done from the reference
    study \cite{zhang_design_2023}. However it is also possible to optimize the electrical
    circuit equivalent using the solvers provided in MATLAB. A method for the development
    of a circuit equivalent can be found in \cite{jha_design_2018} and the relationship
    between physical dimensions and the material properties, and the electrical circuit
    components (e.g., the size of the metallic patterns, the thickness and permittivity 
    of the dielectric layers). In greater detail, to define the optimization problem some
    properties of the absorber can be optimized to better maximize the absorbance and to
    do that the objective function is the absorbance itself as in (\ref{eq:Absorbance}) but
    can also be extracted using the $S$ parameters as in (\ref{eq:AbsorbanceSparams}). Any
    constraints on the overall size and spacing will emerge from the optimization.

    \begin{equation}
        \label{eq:AbsorbanceSparams}
        A(\omega) = 1 - |S_{11}(\omega)|^2 - |S_{21}(\omega)|^2 = 1 - R - T
    \end{equation}

    To implement the optimization step using MATLAB two solvers can be invoked.
    \begin{itemize}
        \item \texttt{fmincon} : For constrained nonlinear optimization
        \item \texttt{ga} : For genetic algorithm-based optimization, which can be useful 
            for complex problems with many local optima
    \end{itemize}

    For this study the \texttt{fmincon} shall be chosen and configured with the appropriate
    options:
    \begin{itemize}
        \item Initial State for the design variables
        \item Tolerance for convergence
        \item Maximum number of iterations
    \end{itemize}

    \subsection{\textsf{CST Optimizer}}
        In this study however the optimization step will be performed by the built in optimizer
        in CST. In greater detail the parametric optimizer is used as it can optimize multiple
        parameters at once.

        The parameters chosen to be optimized affect the resistor placement and the area around 
        them as shown in figure (\ref{img:resistors}), these are:
        \begin{itemize}
            \item \texttt{Lh} : The height of resistor placement along the \textsf{z} axis
                with values between 0 and $d=0.035mm$.
            \item \texttt{Oa} : The separation width near the arrows along the $y=x$ line
                with values between $0.001mm$ and $\sqrt{2}mm$.
            \item \texttt{Oo} : The separation with near the ring along the circle that has a 
                radius of $r=r_1+\frac{(r_2-r1)}{2}$, with $r_1=2mm$ and $r_2=2.7mm$ and with 
                values between $0.001mm$ and $0.1mm$ on each side $0.2mm$ in total.
        \end{itemize}
        
        After the simulation the Absorption is improved as well as the S parameters and
        the aforementioned variables end up with the following values:
        \begin{itemize}
            \item $ Lh = 33.0166 \times 10^3 mm $.
            \item $ Oa = 49.8393 \times 10^3 mm $.
            \item $ Oo = 4.19669 \times 10^3 mm $.
        \end{itemize}

        The optimized S parameters are mentioned in the table of figures (\ref{table:Optimized})
        and in the $S_{11}$, the $S_{21}$ and the exponential term the differences are visibly
        observable \footnote{The refractive index plot has been omitted as the optimization could not 
        have affected it.}. The Absorbance however, even thought it appears to have increased on 
        average across the frequency range, the difference is negligible.

        CST provides a number of different solvers that can set Absorbance maximization as a goal
        function. For this optimization problem the \textsf{Trust Region Framework} is used. It is
        a local optimization solver that can be used globally doing multiple local optimizations for
        all parameters.

        \begin{verbatim}
            Initial goal function value = 0.0882249 (Solver)
            Best goal function value    = 0.0795194 (Solver)
            Last goal function value    = 0.0795194 (Solver)

            Total solver time           = 02:40:38 h (14 solver runs)
            Total data recovery time    = 00:00:31 h (2 loaded)
            Total parameter update time = 00:02:33 h
            Total backup project time   = 00:00:45 h (4 backups)
            Total optimizer time        = 02:44:31 h (16 evaluations)

            Optimization successfully improved the goal value. Best parameter set is stored.
        \end{verbatim}

        It can be observed that the optimizer run 14 times which is considered small for
        three parameters and it is therefore possible to have hit a local minimum.

        \begin{landscape}
            \begin{table}
                \centering
                \begin{tabular}{ccc}
    
                    \begin{tikzpicture}
                        \begin{axis}[ 
                            title={\textsf{Reflection Coefficient}},
                            xlabel={Frequency (GHz)}, ylabel={$S_{11}$},
                            legend pos=south west
                        ] 
                            \addplot table[x=freq, y=s11_Re, col sep=space] {data/Optimized_s11_linear_complex.txt};
                            \addplot table[x=freq, y=s11_Im, col sep=space] {data/Optimized_s11_linear_complex.txt};
    
                            \addlegendentry{$\Re{(S_{11})}$}
                            \addlegendentry{$\Im{(S_{11})}$}
    
                        \end{axis}
                    \end{tikzpicture} &

                    \begin{tikzpicture}
                        \begin{axis}[ 
                            title={\textsf{Reflection Coefficient}},
                            xlabel={Frequency (GHz)}, ylabel={$S_{21}$},
                            legend pos=south west
                        ] 
                            \addplot table[x=freq, y=s21_Re, col sep=space] {data/Optimized_s21_linear_complex.txt};
                            \addplot table[x=freq, y=s21_Im, col sep=space] {data/Optimized_s21_linear_complex.txt};
    
                            \addlegendentry{$\Re{(S_{21})}$}
                            \addlegendentry{$\Im{(S_{21})}$}
    
                        \end{axis}
                    \end{tikzpicture} &
                    
                    \begin{tikzpicture}
                        \begin{axis}[ 
                            title={\textsf{Absorptivity}},
                            xlabel={Frequency (GHz)}, ylabel={A},
                            ymin=0.8, ymax=1 
                        ] \addplot table[x=freq, y=A, col sep=space] {data/Optimized_A.txt};
                        \end{axis}
                    \end{tikzpicture} \\
                    \hline
                    \begin{tikzpicture}
                        \begin{axis}[ 
                            title={\textsf{Permittivity \& Permeability}},
                            xlabel={Frequency (GHz)}, ylabel={$\epsilon_{eff} \& \mu_{eff}$},
                            legend pos=north east 
                        ]   
                            \addplot table[x=freq, y=epsilon_Re, col sep=tab] {data/Optimized_Epsilon_r.txt}; 
                            \addplot[dashed] table[x=freq, y=epsilon_Im, col sep=tab] {data/Optimized_Epsilon_r.txt};
            
                            \addplot table[x=freq, y=mu_Re, col sep=tab] {data/Optimized_Mu_r.txt};
                            \addplot[dashed] table[x=freq, y=mu_Im, col sep=tab] {data/Optimized_Mu_r.txt};
        
                            \addlegendentry{$\Re{(\epsilon)}$}
                            \addlegendentry{$\Im{(\epsilon)}$}
                            \addlegendentry{$\Re{(\mu)}$}
                            \addlegendentry{$\Im{(\mu)}$}
                        
                        \end{axis}
                    \end{tikzpicture} &
    
                    \begin{tikzpicture}
                        \begin{axis}[ 
                            title={\textsf{Intrinsic Impedance}},
                            xlabel={Frequency (GHz)}, ylabel={$z$},
                            legend pos=south east 
                        ] 
                            \addplot table[x=freq, y=z_Re, col sep=tab] {data/Optimized_z_complex.txt};
                            \addplot table[x=freq, y=z_Im, col sep=tab] {data/Optimized_z_complex.txt};
        
                            \addlegendentry{$\Re{(z)}$}
                            \addlegendentry{$\Im{(z)}$}
                        \end{axis}
                    \end{tikzpicture} &
    
                    \begin{tikzpicture}
                        \begin{axis}[ 
                            title={\textsf{Exponential Term}},
                            xlabel={Frequency (GHz)}, ylabel={$e^{-j(\omega t + \beta\hat{z})}$},
                            legend pos=south west
                        ] 
                            \addplot table[x=freq, y=ExpTerm_Re, col sep=tab] {data/Optimized_exp_term.txt};
                            \addplot table[x=freq, y=ExpTerm_Im, col sep=tab] {data/Optimized_exp_term.txt};
        
                            \addlegendentry{$\Re{(e^{-j(\omega t + \beta\hat{z})})}$}
                            \addlegendentry{$\Im{(e^{-j(\omega t + \beta\hat{z})})}$}
                        \end{axis}
                    \end{tikzpicture}
    
                \end{tabular}
                \caption{Absorber Performance Indicators After the Optimization.}
                \label{table:Optimized}
            \end{table}
        \end{landscape}

        
        It is also worth stating that there are parameters that cannot be optimized using the
        method above. While equivalent circuit and transmission line models are valuable tools, 
        they simplify the complex electromagnetic behavior of metamaterial absorbers. 

        \begin{itemize}
            \item \textbf{Fine Geometric Details} : Equivalent circuit models often represent the 
                metamaterial structure with lumped elements. Fine geometric details of the 
                structure (e.g., the exact shape of the metallic patterns, small variations in
                dimensions) that can significantly affect the absorber's performance are not 
                easily captured by these models.
            \item \textbf{Complex Electromagnetic Interactions} : Metamaterials exhibit complex
                electromagnetic interactions, such as near-field coupling between adjacent 
                elements and high-order resonances. These effects may not be fully accounted for 
                in simplified circuit models.
            \item \textbf{Angle of Incidence Effects} : The angle at which the electromagnetic 
                wave hits the absorber can significantly affect its performance. Circuit models
                typically do not incorporate these angle-dependent effects accurately.
            \item \textbf{Polarization Effects} : While some circuit models can be adapted to 
                consider polarization, accurately capturing complex polarization behavior, 
                especially in anisotropic structures, can be challenging.
            \item \textbf{Material Dispersion} : The frequency dependence of the material 
                properties (permittivity and permeability) can be difficult to model precisely 
                with lumped circuit elements, especially over broad frequency ranges.
        \end{itemize}

\section{\textsf{Discussion}}
    \par This study has demonstrated the potential of metamaterial-based microwave absorbers
    for achieving efficient electromagnetic wave absorption. The design and simulation of
    a specific absorber device, inspired by the structure presented \cite{zhang_design_2023},
    highlighted the key factors influencing its performance.
    \par The results of the simulation showcase the ability of the metamaterial absorber to
    achieve high absorptivity across a broad range of frequencies. This is attributed to
    the unique electromagnetic properties of metamaterials, which allow for tailoring the
    absorption characteristics through precise structural design. The multi-layered
    structure of the absorber facilitates broadband absorption by creating multiple
    resonant frequencies.
    \par However, it is important to acknowledge the trade-offs associated with optimizing the
    absorber's performance. For instance, while increasing the connection height between
    the copper faces near the arrows might enhance absorbance, it could also introduce
    additional complexities in the fabrication process. Similarly, achieving a perfect
    impedance match between the absorber and free space is crucial for minimizing
    reflection and maximizing absorption, but this can be challenging to achieve in
    practice due to various factors such as material losses and fabrication tolerances.
    \par In terms of future improvements, there are several avenues to explore. One potential
    direction is to investigate different metamaterial structures and configurations to
    further enhance the absorber's bandwidth and absorption efficiency. For example,
    incorporating additional layers or varying the geometry of the metallic patterns could
    lead to improved performance.
    \par Another area of focus could be on reducing the plasma frequency of metals in
    metamaterials. This would allow the absorbers to operate effectively at even lower
    frequencies, expanding their applicability to a wider range of electromagnetic
    environments.  This can be achieved by manipulating the density of free electron
    carriers in the metal.
    \par Furthermore, exploring alternative modeling methods, such as the transmission line
    equivalent and the electrical circuit equivalent, can provide additional insights into
    the absorber's behavior and aid in the optimization process. These methods offer
    different perspectives on the absorber's performance and can be used to validate the
    simulation results obtained from CST.
    \par In conclusion, this study has provided a comprehensive analysis of a
    metamaterial-based microwave absorber, highlighting its potential for efficient EMI
    mitigation. While there are trade-offs to consider and challenges to overcome, the
    future of metamaterial absorbers is promising. By continuing to explore new designs,
    materials, and modeling techniques, it is possible to further enhance their
    performance and expand their applications in various fields.